---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# syncons

<!-- badges: start -->
<!-- badges: end -->

The goal of `syncons` is to support massive construction of synthetic communities (SynComs) with 24-, 96- and 384-well plates.

## Installation

You can install the development version of `syncons` like so:

``` r
install.packages("pak")
pak::pak("gaospecial/syncons")
```

Now you can use this package.

```{r}
library("syncons")
```

## Layout of SynComs in a plate

A 24-well plate can be used to construct 16 different SynComs with 4 strains.

```{r}
one_plate(24, return_layout = TRUE)
```

A 96-well plate can be used to construct 64 different SynComs with 6 strains.

```{r}
one_plate(96, return_layout = TRUE)
```


A 384-well plate can be used to construct 256 different SynComs with 8 strains.

```{r}
one_plate(384, return_layout = TRUE)
```

## Generation of sample tables

Support we have eight strains and want to construct a series of SynComs with all the possible combinations.

```{r}
strains = paste0("S", 1:8)
assign_plate(strains, plate_type = "96")
```

## Generation of supplementary information

This is for Bio-Protocol submission.

```{r eval=FALSE}
strains = paste0("S", 1:11)
sheets = list(
  sheet1 = assign_plate(strains[1:4]),
  sheet2 = assign_plate(strains[1:5]),
  sheet3 = assign_plate(strains[1:6], plate_type = "96"),
  sheet4 = assign_plate(strains[1:7], plate_type = "96"),
  sheet5_1 = assign_plate(strains[1:8], plate_type = "96"),
  sheet5_2 = assign_plate(strains[1:8], plate_type = "384"),
  sheet6_1 = assign_plate(strains[1:9], plate_type = "96"),
  sheet6_2 = assign_plate(strains[1:9], plate_type = "384"),
  sheet7 = assign_plate(strains[1:10], plate_type = "384"),
  sheet8 = assign_plate(strains[1:11], plate_type = "384")
)

openxlsx::write.xlsx(sheets, file = "Sheets.xlsx")
```

